Efficient Handling of String-Number Conversion

### 2019-11-21 draft.tex
add over-approximation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Over-Approximation} \label{section:over}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our procedure has two steps. In the first step, it replaces all string-number conversion constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints. 
In the second step, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
which constitutes with only integer, membership, and \emph{chain-free} equality constraints. In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
For two equality constraints, 
$\begin{array}{rcll}
	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
	t_2&\defeq& \ldots y \ldots = \ldots&,
\end{array}$\\
we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$. A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
The way to break a chain is simple, one just needs to find any variable $x$ in the dependency circle, and replace it to a fresh variable. Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable to a fresh one, and repeats until all chains are broken.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Over-Approximation} \label{section:over}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our procedure has two steps. In the first step, it replaces all string-number conversion constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints. 
In the second step, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
which constitutes with only integer, membership, and \emph{chain-free} equality constraints. In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
For two equality constraints, 
$\begin{array}{rcll}
	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
	t_2&\defeq& \ldots y \ldots = \ldots&,
\end{array}$\\
we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$. A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable in the dependency circle to a fresh one, and repeats until all chains are broken.
